pema application

### 2022-11-23 paper/manuscript.Rmd
add supplemental tables

abstract: |
  When analyzing a heterogeneous body of literature, there may be many
  potentially relevant between-studies differences. These differences can be
  coded as moderators, and accounted for using meta-regression. However, many
  applied meta-analyses lack the power to adequately account for multiple
  moderators, as the number of studies on any given topic is often low.
  [The present study introduces Bayesian Regularized Meta-Analysis (BRMA),
  which uses regularizing (LASSO or horseshoe) priors to shrink small
  regression coefficients towards zero]{#lassoabstract}, thereby selecting relevant
  moderators from a larger number of candidates.
  This approach is suitable when heterogeneity is suspected,
  but it is not known which moderators most strongly inﬂuence the
  observed effect size.
  We present a simulation study to validate the performance of BRMA
  relative to state-of-the-art random effects meta-analysis using REML (RMA).
  Results indicated that BRMA compared favorably to RMA on three metrics:
  predictive performance (a measure of generalizability),
  the ability to reject irrelevant moderators,
  and the ability to recover population parameters with
  low bias.
  BRMA had slightly lower ability to detect true effects of relevant
  moderators, but the overall proportion of Type I and Type II errors was
  equivalent to RMA. BRMA regression coefficients were slightly
  biased towards zero (by design), but its estimates of residual heterogeneity
  were unbiased. BRMA performed well with as few as 20 studies in the training
  data, suggesting its suitability as a small sample solution. We discuss how
  applied researchers can use BRMA to explore between-studies heterogeneity
  in meta-analysis.
  The method is implemented in the R-package 
  `pema` (penalized meta-analysis) and in the free open source statistical software package JASP.

keywords          : "meta-analysis, machine learning, bayesian, lasso, horseshoe, regularized"
wordcount         : "5356"

bibliography      : ["r-references.bib", "references.bib",
                     "sara-references.bib", "eli-references.bib"]

@@

documentclass     : "apa6"
classoption       : "man"
knit: worcs::cite_essential
output            : papaja::apa6_pdf
---

@@

Meta-analysis is a quantitative form of evidence synthesis,
whereby effect sizes from multiple similar studies are aggregated.
In its simplest form, this aggregation consists of a weighted average of the observed effect sizes.
Weighting accounts for the fact that some observed effect sizes are assumed to be more informative about the underlying population effect.
<!-- Each effect size is assigned a weight that determines how influential it is in calculating the summary effect. -->
The weights are based on specific assumptions;
for example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect.
This assumption is appropriate when meta-analyzing effect sizes from close replication studies [@higginsReevaluationRandomeffectsMetaanalysis2009]. 
The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
<!-- Each observed effect size provides information about the mean and standard deviation of this distribution. -->
This assumption is more appropriate when studies are conceptually similar but vary in small random ways that introduce heterogeneity in effect sizes [@higginsReevaluationRandomeffectsMetaanalysis2009].

Heterogeneity in effect sizes is not always random, however.
When similar research questions are studied by different labs, in different populations, using different study designs, measurement instruments, and methods - those between-study differences may introduce *systematic heterogeneity*.
Suspected causes of systematic heterogeneity can either be used as exclusion criteria,
or accounted for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
Meta-regression estimates the effect of study characteristics on effect size,
and provides an estimate of the overall effect size and residual heterogeneity after controlling for their influence.
For example, if studies have been replicated in Europe and the Americas,
one could either exclude studies from Europe from further analysis,
or code a binary moderator variable called "continent".
One could then estimate the average effect size across both continents.
Similarly, if studies have examined the effect of a drug at different dosages,
one could code dosage as a continuous moderator, and control for its influence - thus estimating the overall effect size at average dosages.

A common application of meta-analysis is to summarize existing bodies of literature.
In such situations, there are many potentially relevant between-study differences that could be coded as moderators.
Although meta-regression can accommodate multiple moderators,
like any regression-based approach, it requires a relatively high number of cases (studies) per parameter to obtain sufficient statistical power.
In applied meta-analyses, the number of available studies is often too low to obtain sufficient power [@rileyInterpretationRandomEffects2011],
or even so low that the model is not identified [@akaikeNewLookStatistical1974].
This problem is known as the "curse of dimensionality".
<!-- This poses a challenge in the -->
<!-- classic meta-analysis paradigm, which, like any regression-based approach, requires a -->
<!-- high number of cases per parameter.  -->
Between-studies differences thus pose a non-trivial challenge to classic meta-analytic methods.
At the same time, they also provide an unexploited
opportunity to learn which factors impact the effect size
found, if adequate exploratory techniques are used.

The curse of dimensionality can be overcome using *variable selection*:
identifying a smaller subset of relevant moderators from a larger number of candidate moderators [@hastieElementsStatisticalLearning2009].
One way to perform variable selection is by relying on theory, and selecting only moderators that should theoretically have an impact on effect size.
Note, however, that theories at the individual level of analysis do not necessarily generalize to the study level of analysis.
In the social sciences, for example, many theories describe phenomena at the level of individual people.
Using such theories for variable selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
To illustrate what a theory at the study level of analysis might look like, 
consider the so-called *decline effect*.
It is a phenomenon whereby effect sizes in a particular tranche of the literature seem to diminish over time [@schoolerUnpublishedResultsHide2011].
It has been theorized that the decline effect can be attributed to regression to the mean:
A finding initially draws attention from the research community because an anomalously large effect size has been published, and subsequent replications find smaller effect sizes.
Based on the decline effect, we might thus expect the variable "year of publication" to be a relevant moderator of study effect sizes.
Note that this prediction is valid even if year is orthogonal to the outcome of interest within each study.
Until more theory about the drivers of between-study heterogeneity is developed,
however, this approach will have limited utility for variable selection.
<!--A second example that might illustrate this problem is a study that concluded that American college students' empathy had decreased over time, based on meta-analysis of 72 samples collected between 1979 and 2009.-->

An alternative solution is to rely on statistical methods for variable selection.
This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
There is precedent for the use of machine learning to perform variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
This prior work used the non-parametric *random forest* algorithm.
One limitation of random forests is that non-parametric models are harder to interpret,
particularly when the readership is accustomed to linear models that describe the effect of each moderator with a single parameter.

Regularization is a method for variable selection that can be applied in linear models.
It effectively shrinks small model parameters towards zero,
such that irrelevant moderators are eliminated.
The present paper introduces *Bayesian regularized meta-regression* (BRMA),
an algorithm that uses Bayesian estimation with regularizing priors to perform variable selection in meta-analysis.
Regularizing priors assign a high probability mass to near-zero values,
which keeps small regression coefficients close to zero, resulting in a sparse solution.
This manuscript discusses two shrinkage priors,
the LASSO and horseshoe prior.
<!--
Thus, there is a need of a regularization method to curtail overfitting. Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection. The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for regularized meta-regression.
This dilemma could be resolved by an exploratory technique that can identify relevant moderators in meta-analysis,
and which is relatively robust to small sample sizes.
-->
<!--Such shrinkage is advantageous because it performs variable selection and results in a sparse model.
Sparse models are easier to interpret, as fewer non-zero effects remain.
Regularization also provides a solution to the curse of dimensionality; unlike standard regression models, it can provide identified models even if the number of moderators exceeds the number of cases.-->
<!--By doing this it automatically performs variable selection. It does not seem to be immediately clear why shrinking the coefficients should be an improvement to the model. However, by shrinking the parameters, it lowers the variance of the model by increasing the bias only a little bit. In other words, the model sacrifices some of its ability to fit the current data, to greatly increase the ability to predict future data with the same fit (James et al., 2013). This is better known as the bias/variance tradeoff (Briscoe & Feldman, 2011).-->

@@

To understand how BRMA estimates the relevant parameters and performs variable selection,
it is instructional to first review the statistical underpinnings of classical meta-analysis.
As mentioned before, the fixed effect model assumes that each observed effect size $T_i$ is an estimate of an underlying true effect size $\Theta$ [@hedgesFixedRandomeffectsModels1998].
The only cause of heterogeneity in observed effect sizes is presumed to be sampling error, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
Thus, for a collection of $k$ studies,
the observed effects sizes of individual studies $i$ (for $i \in [1,2, \ldots k]$) are given by:

\begin{align}
T_i &= \Theta + \epsilon_i\\
\text{where } \epsilon_i &\sim N(0, v_i)
\end{align}

The estimated population effect size $\hat{\theta}$ is then a weighted average of the observed effect sizes.
The assumption that sampling error is the only source of variance in observed effect sizes implies that studies with smaller standard errors estimate the underlying true effect size more precisely and should accrue more weight.
Therefore, fixed effect weights are simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
The estimate of the true effect is a weighted average across observed effect sizes:

\begin{equation}
\hat{\theta} = \frac{\sum_{i=1}^k w_iT_i}{\sum_{i=1}^k w_i}
\end{equation}

<!--A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014). Caused by differences in for example cultures of research populations and used methods or instruments (Neuman, 2011). Even in replication studies there are sometimes moderators that are unanticipated (Kunert, 2016). This leads very often to an eventual poor performance of the fixed effects meta-analysis model (Snijders, 2005). -->

The random effects model assumes that, in addition to sampling error, true effects may vary for random reasons,
and thus follow a (normal) distribution with mean $\Theta$ and variance $\tau^{2}$ [@hedgesFixedRandomeffectsModels1998].
The observed effect sizes are thus given by:

\begin{align}
T_i &= \Theta + \zeta_{i} + \epsilon_i\\
\text{where } \zeta_i &\sim N(0, \tau^2)\\
\text{and } \epsilon_i &\sim N(0, v_i)
\end{align}

As in the fixed effect model,
studies with smaller sampling errors are assigned more weight.
However, to account for the fact that all studies now provide some information about different regions of the distribution of true effect sizes,
the weights are attenuated in proportion to the spread of that distribution.
The random effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
Whereas sampling error is still treated as known,
the between-study heterogeneity $\tau^{2}$ must be estimated.
This estimate is represented by $\hat{\tau}^{2}$.

Meta-regression extends the random effects model to account for systematic sources of heterogeneity, which are coded as moderators.
The equation below describes a model with $p$ moderators, where $x_{1\ldots p}$ represent the moderators, and $\beta_{1\ldots p}$ their regression coefficients.
Note that $\beta_0$ represents the intercept of the distribution of true effect sizes after controlling for the moderators
and the error term $\zeta_{i}$ represents residual unexplained between-studies heterogeneity.
This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random [@lopez-lopezEstimationPredictivePower2014]:

\begin{align}
T_i &= \beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p} + \zeta_{i} + \epsilon_i\\
\end{align}

<!--The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013). The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis \& Reeves, 2011; Jackson \& White, 2018). Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell \& Gorden, 2001). Considering that all models their performance is linked to the accuracy of the estimate. According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
The parameters of this model are the regression coefficients and residual heterogeneity.
Numerous methods have been proposed to estimate meta-regression models,
the most common of which is restricted maximum likelihood (REML).
REML is an iterative method, which means that it repeatedly performs the same calculations and updates the estimated parameters until their estimates stabilize.
<!--, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method. These methods are mostly divided into two groups: closed-form or non-iterative methods and iterative methods. The main difference between these groups is that the closed form group uses a predetermined number of steps to provide an estimation for the residual heterogeneity, whereas the iterative methods run multiple iteration, as the name suggests, to converge to a solution when a specific criterion is met. It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.-->
This estimator has low bias, which means that the average values of the parameters are close to their true values [@panityakulEstimatingResidualHeterogeneity2013].
<!-- ; (Panityakul et al., 2013; Hardy & Thompson, 1996). -->
However, this bias comes at the cost of higher variance, which means that the estimated values of a population parameter vary more from one sample to the next. 
An estimator with low bias and high variance produces results that generalize less well to new data than an estimator with high bias and low variance.
This phenomenon is known as the *bias-variance trade-off*.
Regularization increases bias to reduce variance.
A disadvantage of this trade-off is that model parameters can no longer be interpreted as straightforwardly as OLS regression coefficients.
An advantage is that the resulting model is more generalizable and makes better predictions for new data [see @hastieElementsStatisticalLearning2009].

<!--It needs a starting estimation of $\tau^{2}$, which is usually estimated by one of the non-iterative methods (Viechtbauer \& López-López, 2015). Besides the starting value of $\tau^{2}$, it needs in every iteration an estimation of the regression coefficients of the moderators. These are typically estimated by using the Weighted Least Squares (WLS) method. This is a variation of the Ordinary Least Squares (OLS), but in the case of meta-analysis it is necessary to assess weights to the coefficients. In systematic reviews large variation in standard errors is often observed, which will result in large heteroscedasticity in the estimation of the effects (Stanley \& Doucouliagos, 2017). The addition of weights is a way to adjust for this heteroscedasticity. The weights are formulated as presented in equation (5).-->
<!--
The usage of a WLS method to estimate the regression coefficient may be problematic in the situation where a lot of moderators are measured without their specific effects, when the amount of studies is low and when moderators are dichotomous. The use of a least squares method will cause problems with the prediction accuracy and the model interpretability (James, Witten, Hastie, \& Tibshirani, 2013). In the situation where a lot of moderators are measured and blindly included in the model, it may as well be the case that variables are included that are in fact not associated with the response. Including irrelevant variables in the model lowers the interpretability of the model (James et al., 2013). An approach is necessary that automatically excludes the variables that are irrelevant i.e. performs variable selection. As explained before, in meta-analysis it is often the case that the number of moderators closely approaches or even exceeds the number of studies included in the analysis. A least squares method will display a lot variability in the fit when the number of variables is not much smaller than the number of studies (James et al., 2013). This means that the least squares method over fits the data and loses its power to be generalizable to future observations. When the number of variables exceeds the number of studies, the least squares method fails to produce one unique estimate and the method should not be used at all.

However, a least squares method could still be somewhat valuable in some situations. It is extremely suitable to estimate a linear relationship. In the case of dichotomous moderators, the relationship is always perfectly linear. A powerful non-linear estimation tool is in the situation of dichotomous moderators unnecessary and would not perform better at all. Whenever a non-linear relation gets fitted on data with an underlying linear relation, it will cause problems when this fit gets used for the prediction of future data. Given the various arguments, this paper provides an approach to tackle this problem of the least squares methods whilst still making use of a linear method. The weighted least squares are replaced with the so-called LASSO regression for the estimation of the regression coefficients. This algorithm shrinks or penalizes the regression coefficients and performs variable selection (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008).-->

@@

Ordinary least squares regression (OLS) estimates the model parameters by minimizing the Residual Sum of Squares (RSS) of the dependent variable.
The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data:

$$
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
$$

Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
As an example, we will discuss the most common penalty: the sum of the absolute regression coefficients, also known as the the L1- or LASSO penalty [@hastieElementsStatisticalLearning2009].
Note that other penalties exist.
As the LASSO penalty is a function of the regression coefficients, it increases when they get bigger.
This incentivizes the optimizer to keep the regression coefficients as small as possible.
Note that the amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
If $\lambda$ is zero, the shrinkage penalty has no impact.
If $\lambda \to \infty$,
all coefficients shrink towards zero, producing the null model.
<!--Another commonly used penalty is the L2-norm of the coefficients, or ridge penalty,
which corresponds to the sum of their squared values: $\sum_{j=1}^{p}\beta_{j}^2$.-->
Cross-validation is often used to find the optimal value for the penalty parameter $\lambda$.
<!--The LASSO penalty has the unique property of shrinking some coefficients to be exactly zero,
but the ridge penalty does not do so, as -->
The LASSO penalized residual sum of squares is given by:

$$
PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}|
$$

<!--The Lasso shrinkage method is not the only shrinkage method, there do exist some others. Nevertheless, the lasso is in the case the best option. It possesses, as opposed to other methods, the ability to shrink the parameter not towards zero, but to be exactly zero (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008). This means that the lasso can perform variable selection, something that is specifically aimed for in this study. -->
<!--
**Alternative to linear model: Tree Based models**
An alternative that can perform variable selection, are tree-based models. These kinds of models have numerous other advantages over linear models. Tree-based models can be used for any data type, are easy to represent visually, require little data preparation and got larger power than linear regressions when moderators exceed observations in quantity. They are also more flexible in handling moderator interactions and non-linearity. As a result of that, they are better in modelling the complicated nature of human behaviour (Earp \& Trafimow, 2015). Decision trees split from the top down and group data in so-called ‘sub-nodes’, in which the data’s aspects are most homogeneous. The goal is to split to get the sub-nodes as uniform as possible, which can be until fully homogenous groups, or if a pre-specified touchstone is reached. 
Still, singletree based models have some limitations. First of all, tree models are unstable, small fluctuations that are utilized to make the model have a possibility to lead to considerable alterations in the constructions of the tree (Dwyer \& Holte, 2007). Second, it has problems with seizing linearity, because it only makes ‘twofold splits’ (Steyerberg, 2019). At last, tree-based models are susceptible to overfitting (Hastie et al, 2009).

There are also more complex tree-based models, known as random-forests, which surmount most of the disadvantages of singletree. This variant incorporates multiple decision trees, and combines results from those trees to create a single model with a more accurate estimate (Breiman, 2001). The essential idea behind is know as the ‘wisdom of crowds’, a large number of relatively uncorrelated trees operating as a group will outperform any of the individual elements. The somewhat low correlation between the models is fundamental, because uncorrelated models are able to produce ensemble predictions with a higher accuracy that any individual prediction. This is because the trees preserve each other from their own singular errors (Genuer, Poggi \& Tuleau-Malot, 2010). The lower tendency to overfitting is another advantage of random forests over single trees (Bühlmann \& Yu, 2002). As well as the possibility to predict cases that are not components of the bootstrap sample of the tree. This kind of measure is known as out-of-bag error, which is an approximation of the cross-validation error, and provides proper estimates of the prediction accuracy in further samples (Hastie et al., 2009). 
An alternative to explore heterogeneity in meta-analysis with a singletree-based method is MetaForest. A technique developed by van Lissa (2017), designed to overcome the lacking’s of singletrees by using random forests. MetaForest applies random effects or fixed effects weights to random forests.
Based on two simulation studies, van Lissa (2017) examined the performance of fixed effects, random effects and unweighted MetaForest.

The study displayed also other advantages from random forests over singletrees. It had greater power, was able to make better predictions, gave estimates of the cross-validation error and yielded useful measures of variable importance and partial prediction plots (van Lissa, 2017). MetaForest can at the moment be considered as the best working technique to explore heterogeneity in meta-analysis. In van Lissa (2017), that only presented estimates of $\tau^{2}$ based on the raw data, we saw that MetaForest had certain robustness against a low number of studies. If moderators were continuously distributed, MetaForest had sufficient power at approximately 20 studies. However, there is an important feature to prove before we can make such an assumption. The underlying data generating models in the two simulation studies of van Lissa (2017) only included normal distributed moderators. Renouncing from normal distributions may affect the performance of the model, but since normal distribution in real-life data is more an exception than a normal state of affairs (Micceri, 1989), it is entirely possible that procedures are affected by skewness, leverage, balance etc. It is important to know how MetaForest performs in these kinds of situations.-->

@@

An alternative to the use of a shrinkage penalty is Bayesian estimation with a regularizing prior.
Bayesian estimation combines information from the data with a *prior distribution*.
The prior distribution assigns a-priori probability to different parameter values.
Likely parameter values have a high probability density, and unlikely parameter values have a low probability density.
The aforementioned (frequentist) approaches, by contrast, treat every possible parameter value as equally plausible.
The prior distribution is updated with the likelihood of the data to form a posterior distribution,
which reflects expectations about likely parameter values after having seen the data [for an extensive introduction, see @mcelreathStatisticalRethinkingBayesian2020].

>>>>

abstract: |
  When meta-analyzing heterogeneous bodies of literature,
  meta-regression can be used to account for potentially relevant between-studies differences.
  A key challenge is that the number of these potential moderators is often high
  relative to the number of studies.
  This introduces a risk of overfitting and finding spurious results.
  To overcome this challenge,
  [we introduce Bayesian Regularized Meta-Analysis (BRMA),
  which selects relevant moderators from a larger set of candidates
  by shrinking small regression coefficients towards zero
  with regularizing (LASSO or horseshoe) priors.]{#lassoabstract}
  This method is suitable when there are many potential moderators,
  but it is not known beforehand which of them are relevant.
  A simulation study compared BRMA against state-of-the-art random effects
  meta-regression using restricted maximum likelihood (RMA).
  Results indicated that BRMA outperformed RMA on three metrics:
  BRMA had superior predictive performance, which means that the results
  generalized better;
  BRMA was better at rejecting irrelevant moderators,
  and worse at detecting true effects of relevant
  moderators,
  but the overall proportion of Type I and Type II errors was
  equivalent to RMA.
  BRMA regression coefficients were slightly biased towards zero (by design),
  but its residual heterogeneity estimates were less biased than those of RMA.
  BRMA performed well with as few as 20 studies,
  suggesting its suitability as a small sample solution. 
  We present free open source software implementations in the R-package `pema` (for penalized meta-analysis)
  and in the stand-alone statistical program JASP.
  An applied example demonstrates the use of the R-package.

keywords          : "meta-analysis, machine learning, regularization, bayesian, lasso, horseshoe"
wordcount         : "5356"

bibliography      : ["r-references.bib", "references.bib",
                     "sara-references.bib", "eli-references.bib", "metaforest.bib"]

@@

documentclass     : "apa6"
classoption       : "man"
knit: worcs::cite_essential
output            : papaja::apa6_pdf
header-includes:
  - \raggedbottom
---

@@

<span id = "openingparagraph">A common application of meta-analysis is to summarize existing bodies of literature.
A crucial challenge is that there is often substantial heterogeneity between studies,
because similar research questions are studied in different labs,
sampling from different populations,
and using different study designs, instruments, and methods.
Any of those between-studies differences can introduce *systematic heterogeneity* in observed effect sizes.
Suspected causes of systematic heterogeneity can either be used as exclusion criteria,
or controlled for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
The latter approach provides an opportunity to learn which factors impact the effect size
found.
However, a limitation of meta-regression is that it requires a relatively high number of cases (studies) per parameter to obtain sufficient statistical power.
In applied meta-analyses, the number of available studies is often low [@rileyInterpretationRandomEffects2011].
This introduces a risk of overfitting,
which results in uninterpretable model parameters [@hastieElementsStatisticalLearning2009].
In extreme cases, the ratio of cases to parameters can be so low that the model is not (empirically) identified,
resulting in non-convergence [@akaikeNewLookStatistical1974].
Accounting for between-studies heterogeneity thus poses a non-trivial challenge to classic meta-analytic methods.
The present study introduces a novel method that overcomes this challenge by imposing Bayesian regularizing (LASSO and horseshoe) priors on the regression coefficients.
These priors shrink the effect of irrelevant predictors towards zero while leaving important predictors relatively unaffected.
The result is a sparse model with fewer non-zero parameters,
which benefits model convergence, reduces overfitting, and helps identify relevant between-study differences.
</span>

## Variable selection

The "curse of dimensionality" refers to the aforementioned problems that arise when the number of moderators is high relative to the number of cases [@hastieElementsStatisticalLearning2009].
It can be overcome by performing *variable selection*:
identifying a smaller subset of relevant moderators from the larger set of candidate moderators [@hastieElementsStatisticalLearning2009].
<span id = "theory">One way to perform variable selection is by relying on theory,
and selecting only moderators that should theoretically have an impact on effect size.
An important caveat is that theories that describe phenomena at the level of individual units of analysis do not necessarily generalize to the study level.
Using such theories for variable selection amounts to committing the ecological fallacy:
generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
The implications of the ecological fallacy for interpreting the *results* of meta-regression have been discussed elsewhere [@bakerUnderstandingHeterogeneityMetaanalysis2009]:
For example, meta-regression may find a significant positive effect of average sample age on treatment efficacy,
even if age is uncorrelated with treatment effect within each study.
A similar problem arises when using individual level theory to select study level moderators:
If theory states that an individual's age influences their susceptibility to treatment,
that does not imply that average sample age will be a relevant moderator of study-level treatment effect in meta-regression.
For an example of study level theory,
consider the *decline effect*:
effect sizes in any given tranche of the literature tend to diminish over time [@schoolerUnpublishedResultsHide2011].
When, by coincidence, a large effect is found, it initially draws attention from the research community.
Subsequent replications then find smaller effects due to regression to the mean.
Based on the decline effect, we might hypothesize "year of publication" to be a relevant moderator of study effect sizes.
At present, few such study level theories about the drivers of heterogeneity exist, and until they are developed,
theory has limited utility for variable selection.</span>

An alternative solution is to rely on statistical methods for variable selection.
This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
There is precedent for the use of machine learning to perform variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
This prior work used the non-parametric *random forest* algorithm to perform variable selection.
One limitation of random forests is that non-parametric models are harder to interpret,
particularly when the readership is accustomed to linear models that describe the effect of each moderator with a single parameter.

In linear models, variable selection can be accomplished via a statistical method called  *regularization*.
Regularization shrinks small model parameters towards zero,
such that irrelevant moderators are eliminated.
Different approaches to regularization exist [@hastieElementsStatisticalLearning2009].
<span id = "lassointroduction">The present paper introduces *Bayesian Regularized Meta-Regression* (BRMA),
an algorithm that uses Bayesian regularizing priors to perform variable selection in meta-analysis.
Regularizing priors assign a high probability density to near-zero values,
which shrinks small regression coefficients towards zero, thus resulting in a sparse solution.
This manuscript discusses two shrinkage priors,
the LASSO and horseshoe prior.</span>

@@

To understand how BRMA estimates the relevant parameters and performs variable selection,
it is instructional to first review the statistical underpinnings of classical meta-analysis.
In its simplest form, meta-analysis amounts to computing a weighted average of the effect sizes.
Each effect size is assigned a weight that determines how influential it is in calculating the summary effect.
The weights are based on specific assumptions.
For example, the *fixed effect* model assumes
that each observed effect size $T_i$ is an estimate of an underlying true population effect size $\beta_0$ [@hedgesFixedRandomeffectsModels1998].
This assumption is appropriate when meta-analyzing close replication studies [@higginsReevaluationRandomeffectsMetaanalysis2009].
The only cause of heterogeneity in observed effect sizes is presumed to be sampling error, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
Thus, for a collection of $k$ studies,
the observed effects sizes of individual studies $i$ (for $i \in [1,2, \ldots k]$) are given by:
\begin{align}
T_i &= \beta_0 + \epsilon_i\\
\text{where } \epsilon_i &\sim N(0, v_i)
\end{align}
The estimated population effect size $\hat{\beta_0}$ is then a weighted average of the observed effect sizes.
The assumption that sampling error is the only source of variance in observed effect sizes implies that studies with smaller standard errors estimate the underlying true effect size more precisely and should accrue more weight.
Therefore, fixed effect weights are simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
The estimate of the true effect is a weighted average across observed effect sizes:
\begin{equation}
\hat{\beta_0} = \frac{\sum_{i=1}^k w_iT_i}{\sum_{i=1}^k w_i}
\end{equation}

The *random effects* model, by contrast, assumes that,
in addition to sampling error, true effects vary for random reasons,
and thus follow a normal distribution with mean $\beta_0$ and variance $\tau^{2}$ [@hedgesFixedRandomeffectsModels1998].
This assumption is appropriate when studies are conceptually similar but differ in small random ways [@higginsReevaluationRandomeffectsMetaanalysis2009]. 
The observed effect sizes are thus given by:
\begin{align}
T_i &= \beta_0 + \zeta_{i} + \epsilon_i\\
\text{where } \zeta_i &\sim N(0, \tau^2)\\
\text{and } \epsilon_i &\sim N(0, v_i)
\end{align}
As in the fixed effect model,
studies with smaller sampling errors are assigned more weight.
However, to account for the fact that all studies now provide some information about different regions of the distribution of true effect sizes,
the weights are attenuated in proportion to the spread of that distribution.
The random effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
Whereas sampling error is still treated as known,
the between-study heterogeneity $\tau^{2}$ must be estimated.
This estimate is represented by $\hat{\tau}^{2}$.

Between-studies heterogeneity is not always random, however.
Meta-regression extends the random effects model to account for systematic sources of heterogeneity,
which are coded as moderators.
It estimates the effect of moderators on effect size,
and provides an estimate of the overall effect size and residual heterogeneity after controlling for their influence.
For example, if studies have been conducted in Europe and the Americas,
one could code a binary moderator variable called "continent".
Using meta-regression, one can then estimate either the continent-specific effect size,
or control for the difference between continents when estimating the overall average effect size.
Similarly, if studies have examined the effect of a drug at different dosages,
one could code dosage as a continuous moderator and estimate the overall effect size at average dosages,
or at a specific dosage.
The equation below describes a general model for $p$ moderators,
where $x_{1\ldots p}$ represent the moderator variables,
and $\beta_{1\ldots p}$ their regression coefficients.
Note that $\beta_0$ represents the intercept of the distribution of true effect sizes after controlling for the moderators
and the error term $\zeta_{i}$ represents residual unexplained between-studies heterogeneity.
This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random [@lopez-lopezEstimationPredictivePower2014]:
\begin{align}
T_i &= \beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p} + \zeta_{i} + \epsilon_i\\
\end{align}

<!--The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013). The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis \& Reeves, 2011; Jackson \& White, 2018). Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell \& Gorden, 2001). Considering that all models their performance is linked to the accuracy of the estimate. According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
Numerous methods have been proposed to estimate meta-regression models,
the most common of which is restricted maximum likelihood [REML, @pattersonRecoveryInterblockInformation1971].
REML is an iterative method, which means that it repeatedly performs the same calculations and updates the estimated parameters until their estimates stabilize.
This estimator has low bias, which means that the average values of the parameters are close to their true values [@panityakulEstimatingResidualHeterogeneity2013].
However, this bias comes at the cost of higher variance, which means that the estimated values of a population parameter vary more from one sample to the next. 
An estimator with low bias and high variance produces results that generalize less well to new data than an estimator with high bias and low variance.
This phenomenon is known as the *bias-variance trade-off*.
Regularization increases bias to reduce variance.
A disadvantage of this trade-off is that model parameters can no longer be interpreted as straightforwardly as OLS regression coefficients.
An advantage is that the resulting model is more generalizable and makes better predictions for new data [see @hastieElementsStatisticalLearning2009].

@@

Ordinary least squares regression (OLS) estimates the model parameters by minimizing the Residual Sum of Squares (RSS) of the dependent variable.
The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data:
$$
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
$$
Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
As an example, we will discuss the most common penalty: the sum of the absolute regression coefficients, also known as the the L1- or LASSO penalty [@hastieElementsStatisticalLearning2009].
Note that other penalties exist.
As the LASSO penalty is a function of the regression coefficients, it increases when they get bigger.
This incentivizes the optimizer to keep the regression coefficients as small as possible.
Note that the amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
If $\lambda$ is zero, the shrinkage penalty has no impact.
As $\lambda$ increases,
all coefficients shrink towards zero, ultimately producing the null model.
Cross-validation is often used to find the optimal value for the penalty parameter $\lambda$.
The LASSO penalized residual sum of squares is given by:
$$
PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}|
$$

@@

<span id = "morepriors">An alternative to the use of a shrinkage penalty is Bayesian estimation with a regularizing prior.
Whereas the aforementioned (frequentist) approaches treat every possible parameter value as equally plausible,
Bayesian estimation combines information from the data with a *prior distribution* that assigns a-priori probability to different parameter values.
Likely parameter values have a high probability density, and unlikely parameter values have a low probability density.
The prior distribution is updated with the likelihood of the data to form a posterior distribution,
which reflects expectations about likely parameter values after having seen the data [for an extensive introduction, see @mcelreathStatisticalRethinkingBayesian2020].
